\setcounter{section}{1}
\section{2024年09月}

\item {
    If \underline{\hbox to 20mm{}} (ask) what my best memory of school is, I'd have to say it's when I won first prize in a singing contest. 
    % asked
} 
\item {
    Submit your essay ahead of time, \underline{\hbox to 20mm{}} you?
    % will/won't
} 
\item {
    If \underline{\hbox to 20mm{}} I have seen it with my own eyes!
    % only
} 
\item {
    He has become calmer when \underline{\hbox to 20mm{}} (face) difficulties through his new hobby.
    % faceing
} 
\item {
    Nobody should go through that bullying, \underline{\hbox to 20mm{}} he?
    % should
} 
\item {
    When \underline{\hbox to 20mm{}} (think) of pyramids, we think of Egypt. But Central America is home to hundreds of these huge ancient structures.
    % thinking
} 
\item {
    Does anyone have superpowers? And if \underline{\hbox to 20mm{}}, what super powers would you all like to have?
    % not
} 
\item {
    Art is never created for making money, \underline{\hbox to 20mm{}} it?
    % is
} 
\item {
    You must have heard about the inspiring news yesterday,  \underline{\hbox to 20mm{}} you?
    % didn't
} 
\item {
    \underline{\hbox to 20mm{}} creative ways they use their family photos!
    % What
} 
\item {
    I don't think it's a good idea to put so much pressure on children at such a young age, \underline{\hbox to 20mm{}} it?
    % is
} 
\item {
    \underline{\hbox to 20mm{}} I wish I could fulfill my original intention in the fulture!
    % How
} 
\item {
    \underline{\hbox to 20mm{}} great pressure professional players withstand while competing in tournament around the world!
    % What
} 
\item {
    Could we succeed in removing my name finally? If \underline{\hbox to 20mm{}}, in what way?
    % so
} 
\item {
    They have achieved  better results in the exam than \underline{\hbox to 20mm{}} (I).
    % I
} 
\item {
    It doesn't matter if she wants to come to your party, \underline{\hbox to 20mm{}}?
    % does it
} 
\item {
    When you finish reading the book, don't forget to put it back on the shelf, \underline{\hbox to 20mm{}}?
    % will you
} 
\item {
    \underline{\hbox to 20mm{}} different life today is from what it was fifty years ago!
    % How
} 
\item {
    On weekends, Kelly helped her mother a lot with housework. \underline{\hbox to 20mm{}} hard word she has done!
    % What
} 
\item {
    He can learn to refuse others if \underline{\hbox to 20mm{}} (encourage).
    % encouraged
} 
\item {
    There is no limit to what you can do if you are hardworking,  \underline{\hbox to 20mm{}}?
    % is there
} 
\item {
    \underline{\hbox to 20mm{}} (be) sure to review what you learn every day, which is of great benefit to your study.
    % Be
} 