\setcounter{section}{1}
\section{2024年09月}

\item {
    The blood samples have been sent away for \underline{\hbox to 20mm{}} (analyze). 
    % analysis
}

\item {
    The seaside had all sorts of pleasant \underline{\hbox to 20mm{}} (associate) with childhood holidays for me. 
    % associations
}

\item {
    Kunqu Opera, \underline{\hbox to 20mm{}} (originate) in the late Yuan and early Ming Dynasties, first emerged as \underline{\hbox to 20mm{}} unique local melody in the eastern Chinese city of Suzhou. Thanks to reforms by a retired official named Wei Liangfu, it took a delicate form in the 1500s, \underline{\hbox to 20mm{}} it earned its reputation as "The Queen of the Chinese Operas".

    Kunqu Opera is a \underline{\hbox to 20mm{}} (mix) of various art forms including songs, narration, dance and martial arts, with astonishing makeup, embroidered costumes and stage arrangements adding to its elegance. \underline{\hbox to 20mm{}} many traditional Chinese operas, the Kunqu style also has five main roles: Sheng, Dan, Jing, Mo, Chou.

    Kunqu Opera performance are highly stylized. Traditionally, the stage is \underline{\hbox to 20mm{}} (simple) decorated so as not to steal the show from the production's most important element: the plot. The storyline \underline{\hbox to 20mm{}} while performing, \underline{\hbox to 20mm{}} performers need to do is control their breath and tone with extreme carefulness, has full command of their \underline{\hbox to 20mm{}} (face) expressions and master the many ways to use their stares, smiles and frowns to convey their emotions.

    The basic performance unit of Kunqu Opera, Qupai, is still in use in some traditional operas and is expected \underline{\hbox to 20mm{}} (use) in the future.
    % when, mixture, driven, what, facial
}