\section{202412}
\item{
    They find a sign \underline{\hbox to 10mm{}} a tree. And they also find a bird \underline{\hbox to 10mm{}} the tree.
           
    \begin{tabular}{rcl}
        \makebox[3em][s]{A. in; in}  & \hspace{6em} & {B. on; on} \\
        \makebox[3em][s]{C. on; in} & \hspace{6em} & {D. in; on}\\
    \end{tabular}
    % C
} 
\\
\item{
    Mr and Mrs Smith open a small \underline{ 1 } in America. To attract people, they put a notice on the door, and \underline{ 2 } says, "Meals on the House for Three Days."

    \hspace{2em} 
    A Chinese student comes to the US and he doesn't know \underline{ 3 } English. On Monday after he has afternoon classes, he walks past the restaurant. It is time for dinner and he feels very hungry. "Well, I am going to have \underline{ 4 } to eat." When he walks to the restaurant, he sees the notice. "American people are really \underline{ 5 }. They even have meals on the house! But \underline{ 6 } can I get to top of the house?" he thinks.

    \hspace{2em} 
    He looks around and finds a ladder \underline{ 7 } the restaurant. He is very happy. But when he gets to the top, he hears someone shouting at him. "Hey! What are you doing there?" Mr Smith and a policeman are standing there and \underline{ 8 } him. "Doesn't your notice say 'Meals on the House for Three Days'? Is it \underline{ 9 } a joke?" the student asks. When Mr Smith and the policeman hear this, they start laughing. "Do you know what 'ON THE HOUSE' means? It means you don't have to give money for the meal! It's \underline{ 10 }!" the policeman says.

    \begin{tabular}{lllll}
        \makebox[5em][l]{(1) A. hotel}&\hspace{1em}&{B. shop}&\hspace{1em}&{C. restaurant}\\
        \makebox[5em][l]{(2) A. they}&\hspace{1em}&{B. he}&\hspace{1em}&{C. it}\\
        \makebox[5em][l]{(3) A. many}&\hspace{1em}&{B. much}&\hspace{1em}&{C. little}\\
        \makebox[6em][l]{(4) A. something}&\hspace{1em}&{B. anything}&\hspace{1em}&{C. nothing}\\
        \makebox[5em][l]{(5) A. happy}&\hspace{1em}&{B. interesting}&\hspace{1em}&{C. warm}\\
        \makebox[5em][l]{(6) A. why}&\hspace{1em}&{B. where}&\hspace{1em}&{C. how}\\
        \makebox[5em][l]{(7) A. to}&\hspace{1em}&{B. near}&\hspace{1em}&{C. on}\\
        \makebox[7em][l]{(8) A. looking for}&\hspace{1em}&{B. staying with}&\hspace{1em}&{C. looking at}\\
        \makebox[5em][l]{(9) A. only}&\hspace{1em}&{B. hardly}&\hspace{1em}&{C. always}\\
        \makebox[5em][l]{(10) A. well}&\hspace{1em}&{B. free}&\hspace{1em}&{C. long}\\
    \end{tabular}
} 
\\